### 2019-03-19 _publications/jors/paper.tex
Add funding statement
Update for tkphd review

\section*{Title}

PFHub: The Phase-Field Community Hub

\url{https://pages.nist.gov/pfhub}

@@

The entire environment can be built using the Nix Package Manager so
the only required dependency is a functional Nix installation. The
full set of dependencies are extensive and fully outlined in the Nix
recipe stored in the repository~\cite{nix-recipe}.

@@

Ask Jim for this text.

>>>>

\section{Title}
\par\bigskip
PFHub: The Phase-Field Community Hub\\[\baselineskip]
\url{https://pages.nist.gov/pfhub}

@@

The entire environment can be built using the Nix Package Manager so
the only required dependency is a functional Nix installation. The
PFHub framework has over 2000 separate package dependencies using
data from the Nix package manager. The full dependency graph for PFHub
can be seen online~\cite{dependencies}.

@@

D.W. wishes to acknowledge the Materials Genome Initiative funding
allocated to the National Institute of Standards and Technology.
